### 2016-07-15 forgerard.tex
quadratic model5

\begin{equation*}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_0 D \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_1 D  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_2 D \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_3 D \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_4 D 
\end{matrix}
\right)
,C_{c}
\right).
\end{equation*}
\begin{equation*}
D \sim \mathcal{N}(0,1)
\end{equation*}
\begin{equation*}
\left(
\begin{matrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\end{equation*}

>>>>

\begin{equation*}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\rho_{00} R +\rho_{10} R^2\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\rho_{01} R  +\rho_{11} R^2\\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\rho_{02} R +\rho_{12} R^2\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\rho_{03} R +\rho_{13} R^2\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\rho_{04} R +\rho_{14} R^2
\end{matrix}
\right)
,C_{c}
\right).
\end{equation*}
\begin{equation*}
R \sim \mathcal{N}(\bar{R},1)
\end{equation*}
\begin{equation*}
\left(
\begin{matrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\end{equation*}
